Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 policies.tex
Discussion on sub-flow dropping.

% Our goal with enabling partial monitoring is to allow for a specified overhead target or budget to be met while maximizing the amount of monitoring performed.
% This is done by dynamically dropping a portion of the monitoring operations. In this section, we discuss in detail how this dropping decision is
% made. Specifically, we first discuss how to decide when dropping should be performed 
% Section~\ref{sec:policies.slack}. Next, we investigate trade-offs created by
% selecting which events are dropped (Section~\ref{sec:policies.events}). Different policies in determining which
% events can be dropped create a trade-off between how closely the overhead
% budget is met and the monitoring coverage achieved.

@@

% % Slack tracking module
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/stm.pdf}
%     \vspace{-0.2in}
%     \caption{Slack tracking and drop decision hardware.}
%     \label{fig:policies.stm}
%     \vspace{-0.1in}
%   \end{center}
% \end{figure}

% Figure~\ref{fig:policies.stm} shows a hardware slack tracking module for
% keeping track of slack. 
Slack can be easily measured in hardware by using a counter that increments on every $k$-th
cycle of the main core (e.g., every 5th cycle for a 20\% target budget). 
% This $k$ can be calculated by taking the reciprocal of
% the target budget. For example, if the target budget is 20\%, then the counter
% increments on every 5th clock cycle. 
The value of this counter is the
accumulated slack. Whenever the main core is stalled due to the monitor, the
measured slack is decremented. It is difficult to precisely determine the
entire impact of monitoring on the main core due to the
difficulty in measuring certain overheads such as contention for shared memory.
However, we have found that using only the stalls due to FIFO back pressure
works well in practice.

@@

% % Varying slack's impact on coverage for UMC
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/dataflow_graph.pdf}
%     \vspace{-0.3in}
%     \caption{Example dependence graph for metadata. Square nodes represent
%     events where checks are performed.} 
%     \label{fig:policies.dataflow_graph}
%     \vspace{-0.1in}
%   \end{center}
% \end{figure}

\begin{figure}
  \begin{center}
  \subfloat[Unrestricted Dropping]{
    \includegraphics[width=\columnwidth]{figs/unrestricted_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[Source-only Dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

@@

An alternative dropping policy which eliminates this wasted work is to only make dropping decisions at
the root or source of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. An example of these source nodes is the
monitoring done to initialize base and bounds information on {\tt malloc} for
an array bounds check. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.

@@

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overheads, then a probabilistic,
source-only dropping policy can be used to provide good total coverage over
multiple runs.

>>>>

% Our goal with enabling partial monitoring is to allow for a specified
% overhead target or budget to be met while maximizing the amount of monitoring
% performed.  This is done by dynamically dropping a portion of the monitoring
% operations. In this section, we discuss in detail how this dropping decision
% is made. Specifically, we first discuss how to decide when dropping should be
% performed Section~\ref{sec:policies.slack}. Next, we investigate trade-offs
% created by selecting which events are dropped
% (Section~\ref{sec:policies.events}). Different policies in determining which
% events can be dropped create a trade-off between how closely the overhead
% budget is met and the monitoring coverage achieved.

@@

% % Slack tracking module \begin{figure} \begin{center}
% \includegraphics[width=\columnwidth]{figs/stm.pdf} \vspace{-0.2in}
% \caption{Slack tracking and drop decision hardware.} \label{fig:policies.stm}
% \vspace{-0.1in} \end{center} \end{figure}

% Figure~\ref{fig:policies.stm} shows a hardware slack tracking module for
% keeping track of slack. 
Slack can be easily measured in hardware by using a counter that increments on
every $k$-th cycle of the main core (e.g., every 5th cycle for a 20\% target
budget). 
% This $k$ can be calculated by taking the reciprocal of the target budget. For
% example, if the target budget is 20\%, then the counter increments on every
% 5th clock cycle. 
The value of this counter is the accumulated slack. Whenever the main core is
stalled due to the monitor, the measured slack is decremented. It is difficult
to precisely determine the entire impact of monitoring on the main core due to
the difficulty in measuring certain overheads such as contention for shared
memory.  However, we have found that using only the stalls due to FIFO back
pressure works well in practice.

@@

% % Varying slack's impact on coverage for UMC \begin{figure} \begin{center}
% \includegraphics[width=\columnwidth]{figs/dataflow_graph.pdf} \vspace{-0.3in}
% \caption{Example dependence graph for metadata. Square nodes represent events
% where checks are performed.} \label{fig:policies.dataflow_graph}
% \vspace{-0.1in} \end{center} \end{figure}

\begin{figure} \begin{center} \subfloat[Unrestricted Dropping]{
\includegraphics[width=\columnwidth]{figs/unrestricted_drop.pdf}
\label{fig:policies.all_drop} } \vspace{-0.1in} \\ \subfloat[Source-Only
Dropping]{ \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
\label{fig:policies.source_drop} } \vspace{-0.1in} \\ \subfloat[Sub-Flow
Dropping]{ \includegraphics[width=\columnwidth]{figs/subflow_drop.pdf}
\label{fig:policies.subflow_drop} } \end{center} \caption{Comparison of
dropping policies using metadata dependence graphs.  Square nodes represent
events where check are performed. Blue (dark) nodes indicate which nodes can be
dropped.} \label{fig:policies.policies} \end{figure}

@@

An alternative dropping policy which eliminates this wasted work is to only
make dropping decisions at the root or source of these metadata flows. That is,
we will decide to either monitor or not monitor an entire metadata flow. An
example of these source nodes is the monitoring done to initialize base and
bounds information on {\tt malloc} for an array bounds check. These source
nodes are typically easy to identify by the dropping hardware because they
correspond to special instructions that are used to set up metadata
information. Thus, it is not necessary to generate and analyze the monitoring
dependence graph to identify source nodes. We refer to this dropping decision
policy as \emph{source-only
dropping} and we refer to the previous policy of dropping any event as
\emph{unrestricted dropping}.

@@

More complex dropping policies can be implemented given more detailed
information about the monitoring dependence graph. Here, we describe one such
policy, which we call \emph{sub-flow dropping}. Sub-flow dropping makes
dropping decisions at a granularity in between unrestricted dropping and
source-only dropping (see Figure~\ref{fig:policies.subflow_drop}). Sub-flow
dropping allows source nodes to be dropped and nodes after branch points in the
monitoring dependence graph to be dropped. From
Figure~\ref{fig:policies.subflow_drop}, this corresponds to nodes {\tt A}, {\tt
C}, and {\tt F}. The basic intuition is that dropping certain portions of the
monitoring dependence graph still result in no wasted work. For example,
dropping node {\tt C} causes nodes {\tt D} and {\tt E} to be skipped. However,
performing monitoring on the remaining nodes allows the check at node {\tt G}
to be performed with no wasted work. Similarly, dropping {\tt F} allows node
{\tt E} to be checked with no wasted work.

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overheads, then a probabilistic,
source-only dropping policy can be used to provide good total coverage over
multiple runs.
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping. Sub-flow dropping matches overheads better than
source-only dropping and provides better coverage than unrestricted dropping.
For a probabilistic policy, sub-flow dropping allows better overhead matching
while still allowing good total coverage over multiple runs, though at a slower
rate than source-only dropping.
